diffusion, websites with 1 pc

### 2023-10-27 src/level_lisa_la.Rmd
presentation

library(tidyverse)
library(rprojroot)
library(rgdal)
library(rgeos)
library(spdep)
library(tmap)
library(maptools)
library(knitr)
library(REAT)
library(tidygeocoder)
library(geosphere)
library(broom)
library(foreach)
library(raster)

@@

```{r}
firms <- read_csv("https://www.nomisweb.co.uk/api/v01/dataset/NM_142_1.data.csv?geography=1811939329...1811939332,1811939334...1811939336,1811939338...1811939428,1811939436...1811939442,1811939768,1811939769,1811939443...1811939497,1811939499...1811939501,1811939503,1811939505...1811939507,1811939509...1811939517,1811939519,1811939520,1811939524...1811939570,1811939575...1811939599,1811939601...1811939628,1811939630...1811939634,1811939636...1811939647,1811939649,1811939655...1811939664,1811939667...1811939680,1811939682,1811939683,1811939685,1811939687...1811939704,1811939707,1811939708,1811939710,1811939712...1811939717,1811939719,1811939720,1811939722...1811939730,1811939757...1811939767&date=latestMINUS10&industry=37748736&employment_sizeband=0&legal_status=0&measures=20100") %>% 
  dplyr::select(GEOGRAPHY_CODE, OBS_VALUE) %>% #GEOGRAPHY_NAME, 
  rename(ladcd = GEOGRAPHY_CODE,
         firms = OBS_VALUE)

@@

Moran I

@@

Website density regressions to London

@@

Website density regressions to the nearest city

@@

Website density regressions to the nearest retail centre

>>>>

library(tidyverse)
library(rprojroot)
# library(rgdal)
# library(rgeos)
library(sf)
library(spdep)
library(tmap)
#library(maptools)
library(knitr)
library(REAT)
library(tidygeocoder)
library(geosphere)
library(broom)
library(foreach)
library(raster)
library(plm)
library(lmtest)

@@

```{r, eval=F}
firms <- read_csv("https://www.nomisweb.co.uk/api/v01/dataset/NM_142_1.data.csv?geography=1811939329...1811939332,1811939334...1811939336,1811939338...1811939428,1811939436...1811939442,1811939768,1811939769,1811939443...1811939497,1811939499...1811939501,1811939503,1811939505...1811939507,1811939509...1811939517,1811939519,1811939520,1811939524...1811939570,1811939575...1811939599,1811939601...1811939628,1811939630...1811939634,1811939636...1811939647,1811939649,1811939655...1811939664,1811939667...1811939680,1811939682,1811939683,1811939685,1811939687...1811939704,1811939707,1811939708,1811939710,1811939712...1811939717,1811939719,1811939720,1811939722...1811939730,1811939757...1811939767&date=latestMINUS10&industry=37748736&employment_sizeband=0&legal_status=0&measures=20100") %>% 
  dplyr::select(GEOGRAPHY_CODE, OBS_VALUE) %>% #GEOGRAPHY_NAME, 
  rename(ladcd = GEOGRAPHY_CODE,
         firms = OBS_VALUE)

@@

## Moran I

@@

## Panel regressions

```{r}
# London
model <- plm(log(n+0.001) ~ log(London+.001)*as.factor(year), 
             data = df,
             index = c("ladcd", "year"),
             model = "within",
             effect = "twoways")
summary(model)

est <- coeftest(model, vcov = vcovHC, type = "HC1") # same
int <- confint(est)

out.model <- bind_cols(tidy(est), 
                       as_tibble(int)) %>% 
  mutate_if(is.numeric, round, 2) %>% 
  mutate(year = 1997:2012) %>% 
  rename(conf.low = '2.5 %',
         conf.high = '97.5 %')

path.out <- paste0(path,"/outputs/lisa/b_panel_dist_london_la.png")
ggplot(out.model, aes(x=reorder(year, year), y=estimate)) +
  geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                    width = 0.2,size  = 1,
                    position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("Interaction coefficients: distance*year, robust st. errors") + xlab("") + 
  ggtitle("Regression coefficients: distance to London on website counts, LA") +
  theme(plot.title = element_text(hjust = 0.5))
ggsave(path.out)

# Cities
model <- plm(log(n+0.001) ~ log(dist+.001)*as.factor(year), 
             data = df,
             index = c("ladcd", "year"),
             model = "within",
             effect = "twoways")
summary(model)

est <- coeftest(model, vcov = vcovHC, type = "HC1") # same
int <- confint(est)

out.model <- bind_cols(tidy(est), 
                       as_tibble(int)) %>% 
  mutate_if(is.numeric, round, 2) %>% 
  mutate(year = 1997:2012) %>% 
  rename(conf.low = '2.5 %',
         conf.high = '97.5 %')

path.out <- paste0(path,"/outputs/lisa/b_panel_dist_cities_la.png")
ggplot(out.model, aes(x=reorder(year, year), y=estimate)) +
  geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                    width = 0.2,size  = 1,
                    position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("Interaction coefficients: distance*year, robust st. errors") + xlab("") + 
  ggtitle("Regression coefficients: distance to Cities on website counts, LA") +
  theme(plot.title = element_text(hjust = 0.5))
ggsave(path.out)

# Retail centres
model <- plm(log(n+0.001) ~ log(dist.retail+.001)*as.factor(year), 
             data = df,
             index = c("ladcd", "year"),
             model = "within",
             effect = "twoways")
summary(model)

est <- coeftest(model, vcov = vcovHC, type = "HC1") # same
int <- confint(est)

out.model <- bind_cols(tidy(est), 
                       as_tibble(int)) %>% 
  mutate_if(is.numeric, round, 2) %>% 
  mutate(year = 1997:2012) %>% 
  rename(conf.low = '2.5 %',
         conf.high = '97.5 %')

path.out <- paste0(path,"/outputs/lisa/b_panel_dist_retail_la.png")
ggplot(out.model, aes(x=reorder(year, year), y=estimate)) +
  geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                    width = 0.2,size  = 1,
                    position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("Interaction coefficients: distance*year, robust st. errors") + xlab("") + 
  ggtitle("Regression coefficients: distance to Retail Centres on website counts, LA") +
  theme(plot.title = element_text(hjust = 0.5))
ggsave(path.out)
```

## Website density regressions to London

@@

## Website density regressions to the nearest city

@@

## Website density regressions to the nearest retail centre
